### 2024-05-27 front_materials/acknowledgments.tex
Fix bib + word trims

I am grateful to my friends at Michigan for the memories in Ann Arbor,
that made this town feel like another hometown in the U.S.
To my family, thank you for your unwavering love and support throughout my life;
your presence has been a constant source of motivation.
Finally, to Eseul Choi, your companionship and unconditional love have made life truly worth pursuing.
Thank you for being by my side.

>>>>

I am grateful to my friends at Michigan for the memories in Ann Arbor,
that made this town feel like another hometown in the U.S.
To my family, thank you for your love and support throughout my life;
your presence has been a constant source of motivation.
Finally, to Eseul Choi, your companionship and unconditional love have made life worth pursuing.
Thank you for being by my side.

### 2024-05-27 out/01. Introduction/01. Moving sofa problem.tex
Fix bib + word trims

The best bounds currently known on \(\mu_{\max}\) are summarized as
\begin{equation}
\label{eqn:best-bounds}
\mu_G := 2.2195\dots \leq \mu_{\max} \leq 2.37.
\end{equation}
The lower bound \(2.2195\dots \leq \mu_{\max}\) comes from Gerver’s sofa \(S_G\) of area \(\mu_G := 2.2195\dots\) constructed in 1994 \autocite{gerverMovingSofaCorner1992} (see \Cref{fig:gerver}). Gerver derived his sofa from local optimality considerations\footnote{Gerver assumed five stages of the movement of a sofa to derive his sofa \(S_G\) \autocite{gerverMovingSofaCorner1992}. While his sofa \(S_G\) is locally optimal (Theorem 2 of \autocite{gerverMovingSofaCorner1992}), this does not eliminate the possibility of a maximum-area sofa with a different kind of movement. Romik’s simplified derivation of \(S_G\) in \autocite{romikDifferentialEquationsExact2018} also relies on the same assumption (Equation 24, p324 of \autocite{romikDifferentialEquationsExact2018}). So their derivations do not constitute a full proof of Gerver’s conjecture \(\mu_{\max} = \mu_G\).} and conjectured \(\mu_G = \mu_{\max}\) that his sofa attains the maximum area. Approximate solutions found by computer experiments are consistent with Gerver’s conjecture.\footnote{Wagner used Monte Carlo simulation to find an approximate solution (Figure 2 of \autocite{wagner1976sofa}) that resembles Gerver’s sofa in shape. More recent approximate solutions, as found by Gibbs \autocite{gibbsComputationalStudySofas} in 2014 and Batsch \autocite{batschNumericalApproachAnalysing2022} in 2022, deviate in area from Gerver’s sofa by small margins of \(1.7 \times 10^{-7}\) and \(5.7 \times 10^{-9}\) respectively.} On the other hand, the upper bound \(\mu_{\max} \leq 2.37\) was proved by Kallus and Romik using extensive computer assistance \autocite{kallusImprovedUpperBounds2018}.

>>>>

The best bounds currently known on \(\mu_{\max}\) are summarized as
\begin{equation}
\label{eqn:best-bounds}
\mu_G := 2.2195\dots \leq \mu_{\max} \leq 2.37.
\end{equation}
The lower bound \(2.2195\dots \leq \mu_{\max}\) comes from Gerver’s sofa \(S_G\) of area \(\mu_G :=
2.2195\dots\) constructed in 1994 \autocite{gerverMovingSofaCorner1992} (see \Cref{fig:gerver}).
Gerver derived his sofa from local optimality considerations\footnote{Gerver assumed five stages of
the movement of a sofa to derive his sofa \(S_G\) \autocite{gerverMovingSofaCorner1992}. While his
sofa \(S_G\) is locally optimal (Theorem 2 of \autocite{gerverMovingSofaCorner1992}), this does not
eliminate the possibility of a maximum-area sofa with a different kind of movement. Romik’s
simplified derivation of \(S_G\) in \autocite{romikDifferentialEquationsExact2018} also relies on
the same assumption (Equation 24, p324 of \autocite{romikDifferentialEquationsExact2018}). So their
derivations do not constitute a full proof of Gerver’s conjecture \(\mu_{\max} = \mu_G\).} and
conjectured \(\mu_G = \mu_{\max}\) that his sofa attains the maximum area. Approximate solutions
found by computer experiments are consistent with Gerver’s conjecture.\footnote{Wagner used Monte
Carlo simulation to find an approximate solution (Figure 2 of \autocite{wagner1976sofa}) that
resembles Gerver’s sofa in shape. More recent approximate solutions, as found by Gibbs
\autocite{gibbsComputationalStudySofas2014} in 2014 and Batsch \autocite{batschNumericalApproachAnalysing2022} in 2022, deviate in area from Gerver’s sofa by small margins of \(1.7 \times 10^{-7}\) and \(5.7 \times 10^{-9}\) respectively.} On the other hand, the upper bound \(\mu_{\max} \leq 2.37\) was proved by Kallus and Romik using extensive computer assistance \autocite{kallusImprovedUpperBounds2018}.
